\section{Trapping Configurations}
Now that we have a better understanding of the types of ions used in trapped ion quantum computing, as well as some of the advantages and disadvantages they each have, we can turn our attention to the trapping configurations. 

When considering the possible geometries that an ion trap can have, we're essentially given two choices: one-dimensional (1D), also known as linear arrays; or two-dimensional (2D), sometimes called planar arrays, which is the basis for the 2D Coulomb crystals we're building up to. 

\subsection{Linear Arrays}
It may come as no surprise that the first quantum computers to be described using trapped ions made use of linear traps. Despite the simplistic geometry, all the necessary features of a quantum computer can be realized with linear ion traps. It's even possible to implement quantum gates between any set of ions in this scheme, not necessarily neighboring ions, for gates involving pairs, triplets, or any arbitrary number of ions. However, in practice, increasing the number of effective qubits is not an arbitrary task. Decoherence due to the environment interacting with the quantum system remains a significant challenge \cite{Cirac}.

Nevertheless, advances have been made that show how linear arrays, through quantum simulation, could provide solutions to difficult problems in materials design and molecular modeling. In 2017, Zhang \textit{et al.} successfully performed a quantum simulation of a dynamical phase transition (DPT) using up to 53 qubits in a linear ion trap. In this system, the qubits are coupled at long-range through their collective quantized motion due to Coulomb interactions \cite{Zhang}.

Communication is not possible. The shuttle has no power. Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems. Assemble a team. Look at records of the Drema quadrant. Would these scans detect artificial transmissions as well as natural signals?

Sensors indicate no shuttle or other ships in this sector. According to coordinates, we have travelled 7,000 light years and are located near the system J-25. Tractor beam released, sir. Force field maintaining our hull integrity. Damage report? Sections 27, 28 and 29 on decks four, five and six destroyed. Without our shields, at this range it is probable a photon detonation could destroy the Enterprise.

Unidentified vessel travelling at sub warp speed, bearing 235.7. Fluctuations in energy readings from it, Captain. All transporters off. A strange set-up, but I'd say the graviton generator is depolarized. The dark colourings of the scrapes are the leavings of natural rubber, a type of non-conductive sole used by researchers experimenting with electricity. The molecules must have been partly de-phased by the anyon beam.

\subsection{Planar Arrays}
These are the voyages of the Starship Enterprise. Its continuing mission, to explore strange new worlds, to seek out new life and new civilizations, to boldly go where no one has gone before. We need to neutralize the homing signal. Each unit has total environmental control, gravity, temperature, atmosphere, light, in a protective field. Sensors show energy readings in your area. We had a forced chamber explosion in the resonator coil. Field strength has increased by 3,000 percent.

Unidentified vessel travelling at sub warp speed, bearing 235.7. Fluctuations in energy readings from it, Captain. All transporters off. A strange set-up, but I'd say the graviton generator is depolarized. The dark colourings of the scrapes are the leavings of natural rubber, a type of non-conductive sole used by researchers experimenting with electricity. The molecules must have been partly de-phased by the anyon beam.

Run a manual sweep of anomalous airborne or electromagnetic readings. Radiation levels in our atmosphere have increased by 3,000 percent. Electromagnetic and subspace wave fronts approaching synchronization. What is the strength of the ship's deflector shields at maximum output? The wormhole's size and short period would make this a local phenomenon. Do you have sufficient data to compile a holographic simulation?

I have reset the sensors to scan for frequencies outside the usual range. By emitting harmonic vibrations to shatter the lattices. We will monitor and adjust the frequency of the resonators. He has this ability of instantly interpreting and extrapolating any verbal communication he hears. It may be due to the envelope over the structure, causing hydrogen-carbon helix patterns throughout. I'm comparing the molecular integrity of that bubble against our phasers.

We're acquainted with the wormhole phenomenon, but this... Is a remarkable piece of bio-electronic engineering by which I see much of the EM spectrum ranging from heat and infrared through radio waves, et cetera, and forgive me if I've said and listened to this a thousand times. This planet's interior heat provides an abundance of geothermal energy. We need to neutralize the homing signal.

Communication is not possible. The shuttle has no power. Using the gravitational pull of a star to slingshot back in time? We are going to Starbase Montgomery for Engineering consultations prompted by minor read-out anomalies. Probes have recorded unusual levels of geological activity in all five planetary systems. Assemble a team. Look at records of the Drema quadrant. Would these scans detect artificial transmissions as well as natural signals?

Exceeding reaction chamber thermal limit. We have begun power-supply calibration. Force fields have been established on all turbo lifts and crawlways. Computer, run a level-two diagnostic on warp-drive systems. Antimatter containment positive. Warp drive within normal parameters. I read an ion trail characteristic of a freighter escape pod. The bomb had a molecular-decay detonator. Detecting some unusual fluctuations in subspace frequencies.

Resistance is futile.